Matching Bullets

### 2015-12-06 imaging-paper.Rnw
added heights of peaks to stats

\paragraph{Acknowledgment}: thanks to the men and women behind R\cite{R}, and the authors of the packages  knitr \cite{knitr} and ggplot2 \cite{ggplot2}.
\section{Conclusion}

>>>>

\paragraph{Acknowledgment} Thanks to the men and women behind the software R\cite{R}, and the authors of the R packages  knitr \cite{knitr} and ggplot2 \cite{ggplot2}.
\section{Conclusion}
